Quantum Computing and its Implications on Digital Security

### 2021-12-14 paper.tex
feat: Add page numbers to citations

\begin{subsection}{Ion Traps}
Vedral and Plenio describe the workings of the ion trap in their paper \cite{2008} as follows. 
They state that the ion trap quantum computer represents qubits in energy states and in vibrational modes between ions. 
In a linear ion trap, currents in electrodes generate a time dependent electric field. 
Ions then move through this potential and for some currents and ion masses, the ions get trapped in the field. 
The equilibrium is caused by the force from the electric field generated by the electrodes and the electrostatic repulsion of the ions. 
The ions form a string seperated by only a few wavelengths of light. 
The distance of a few wavelengths is sufficient to operate each ion with a different laser. 
A challenge the researchers faced when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
In general, the ions are trapped at their position but they are in fact not resting but oscillating around their equilibrium position. 
The ions then get cooled by using laser cooling to reduce the movement of the ions in their current position. 
This process is able to cool down the ions near 0 Kelvin. 
At this point, the only movement left would be the movement caused by the quantum mechanical uncertainty priciple. 
So far, it is not possible to cool a whole string of ions to near 0 K, 
although several attempts cooling down a single ion and two ions succeeded.

As mentioned by Prashant in his paper \cite{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
This achievment lead to Shor's factoring algorithm, 
which is based on performing Fourier transforms.

@@

\begin{subsection}{Nuclear Magnetic Resonance}
As explained in the article by Gershenfeld \cite{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
Each molecule in the liquid represents an quantum memory register. 
NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
In an NMR quantum computer, qubits are represented as spin states of the atoms in the molecules. 
In contrast to the ion trap quantum computer, 
a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register.

@@

NMRs have been succesfully used in quantum computing, as they can solve non-polynomial problems in a polynomial time.
According to Gershenfeld \cite{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
which will be covered in the respective chapter. 
\end{subsection}

\begin{subsection}{Josephson Junctions}
As Martinis and Osborne explain in their paper, 
the Josephson effect is a phenomenon that occurs when two superconductors are seperated 
by some barrier or restriction between them, which is thin enough that electrons can tunnel through the barrier using quantum-mechanics. 
This tunneling produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
This is used to create a non-linear inductance and design the qubits. 
Wendin and Shumeiko mention \cite{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
The josephson energy comes from kinetic energy of the tunneling electrons.

Martinis and Osborne state \cite{martinis} that Josephson junction quantum computers are especially interesing because superconductor could provide long coherence times and because increasing the number of qubits should be straightforward.

@@

\begin{itemize}
    \item Often, as e.g. in the Josephson junction quantum computer, extremely low temperatures are needed. These have to be achieved at reasonable cost. Using e.g. laser cooling is a one approach in quantum computing. The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D. Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
    \item Quantum algorithms have probabilistic characteritics. 
    This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
    Figuring out the correct answer reduces the potential speed of quantum computers.
    \item Qubits are prone to errors earlier introduced as noise. 
    Noise can be caused e.g. by heat or noise in the environment. 
    As in classical computing, this noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
    One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
    \item Increasing the number of qubits in a processor. The more qubits in a processor, the more logical qubits can be used. More qubits also lead to less errors since methods for error correction can be used more effectively.
    \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
    According to Mavroeidis \cite{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
    Their qubits remained in superposition for a total of 35 seconds.
\end{itemize}

@@

\begin{subsection}{Shor's algorithm}
Shor's algorithm is a quantum computer algorithm and got developed by Peter Shor in 1994.
Essentially, it can find the prime factors of an integer in the complexity class BQP,
which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $\frac{1}{3}$ for all instances. 
Shor's algorithm is nearly exponentially faster than the general number field sieve, which is the most efficient known classical factoring algorithm.
The efficiency of the quantum Fourier transform which, as earlier discussed, can be caluclated using e.g. an ion trap quantum computer, is responsible for the efficiency of Shor's algorithm.
The algorithm is generally capable to break current public-key cryptography mechanisms as RSA or the Diffie-Hellman key exchange if the quantum computer could operate with little noise. 
That these algorithms could be vulnerable was already stated by Kirsch in 2015
\cite{Kirsch2015QuantumCT}.

Bone and Castro \cite{Bone} describe the workings of Shor's algorithm as follows. First, a memory register is placed into a superposition of all its possible states. Think of all possible permutations of $n$ bits existing in parallel.
A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every of the permutations generated before. 
They then describe the mathematics performed on the registers: 
\begin{itemize} 
    \item N describes the integer to be factorized
    \item X is a random number in range $1 < X < N-1$
    \item X is raised to one of the permutations generated earlier.
    \item The remainder of this operation is placed in a second register. The first register contains the permutation.
\end{itemize}
After performing these operations on all permutations, it is noticable that the contents of the second register repeat e.g. for $N = 15$ the repeating sequence would be $1,2,4,8,1,2,4...$.
Now the frequency of repetition can be calculated by using a complex operation on the second register and the looking at the contents which causes the results from every permutation to interfere. A possible prime factor can then be calculated by using the frequency of repetition $f$:
\begin{equation}
Factor P = X^{\frac{f}{2}}-1
\end{equation}
The inteference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering. This cannot be guaranteed! Checking that the resulting number is correct can be achieved by performing a simple multiplication. Repeating the process for different random values X has then a high chance of revealing all prime factors.

@@

As \cite{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search. 
Additionally, Grover's algorithm can be used to improve a lot of brute-force attacks targeting symmetric cryptography.
Brassard proved \cite{1998} that it is possible to combine Grover's algorithm with the birthday paradox, 
also known as a quantum birthday attack, which leads to finding collisions with a complexity of $O(N^{\frac{1}{3}})$.
As a result, many of current , rather weak, hashing alogithms are disqualified for use in the quantum era. 
However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant as even Grover's algorithm does not make it feasible to to find a collision when the keys are too long.
\end{subsection}

@@

\begin{subsubsection}{Lattice-based Cryptography}
Lattice-based Cryptography is a form of public-key cryptography that avoids the weaknesses of RSA and related security mechanisms. 
Rather than multiplying primes, lattice-based encryption schemes involve multiplying matrices. 
As Micciancio and Regev mention in their paper \cite{Micciancio2009}, 
lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems and it is belived that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
which is used in Shor's algorithm cannot be used in lattice-based problems. 
\end{subsubsection}

>>>>

\begin{subsection}{Ion Traps}
Vedral and Plenio describe the workings of the ion trap in their paper \cite[p.12-13]{2008} as follows. 
They state that the ion trap quantum computer represents qubits in energy states and in vibrational modes between ions. 
In a linear ion trap, currents in electrodes generate a time dependent electric field. 
Ions then move through this potential and for some currents and ion masses, the ions get trapped in the field. 
The equilibrium is caused by the force from the electric field generated by the electrodes and the electrostatic repulsion of the ions. 
The ions form a string seperated by only a few wavelengths of light. 
The distance of a few wavelengths is sufficient to operate each ion with a different laser. 
A challenge the researchers faced when trying to realize an ion trap is the mechanical degree of freedom the ions have. 
In general, the ions are trapped at their position but they are in fact not resting but oscillating around their equilibrium position. 
The ions then get cooled by using laser cooling to reduce the movement of the ions in their current position. 
This process is able to cool down the ions near 0 Kelvin. 
At this point, the only movement left would be the movement caused by the quantum mechanical uncertainty priciple. 
So far, it is not possible to cool a whole string of ions to near 0 Kelvin, 
although several attempts cooling down a single ion and two ions succeeded.

As mentioned by Prashant in his paper \cite[p.20]{prashant}, it has been possible to evaluate Fourier transforms using the ion trap quantum computer.
This achievment lead to Shor's factoring algorithm, 
which is based on performing Fourier transforms.

@@

\begin{subsection}{Nuclear Magnetic Resonance}
As explained in the article by Gershenfeld \cite[p.66-71]{Gershenfeld1998QuantumCW}, a nuclear magnetic resonance (NMR) computer consists of a capsule filled with a liquid and an nuclear magnetic resonance spectrometer which is a machine used to analyze the molecular structure of a material by measuring the interaction of nuclear spins when placed in a strong magnetic field.
Each molecule in the liquid represents an quantum memory register. 
NMRs can compute by sending radio signals to the sample using the NMR machine and evaluating the response. 
In an NMR quantum computer, qubits are represented as spin states of the atoms in the molecules. 
In contrast to the ion trap quantum computer, 
a measurement is performed on a statistical ensemble of molecules instead of a single isolated quantum system which was used as memory register.

@@

NMRs have been succesfully used in quantum computing, as they can solve non-polynomial problems in a polynomial time.
According to Gershenfeld \cite[p.69]{Gershenfeld1998QuantumCW}, the first successful computation on a NMR quantum computer was to execute a search using Grover's algorithm, 
which will be covered in the respective chapter. 
\end{subsection}

\begin{subsection}{Josephson Junctions}
As Martinis and Osborne explain in their paper, 
the Josephson effect is a phenomenon that occurs when two superconductors are seperated 
by some barrier or restriction between them, which is thin enough that electrons can tunnel through the barrier using quantum-mechanics. 
This tunneling produces a current, known as supercurrent, that flows continuosly without any voltage applied. 
This is used to create a non-linear inductance and design the qubits. 
Wendin and Shumeiko mention \cite[p.727]{shumeiko} many ways to realize qubits in Josephson junction based quantum computers. 
The simplest of which is to realize qubits in Josepshon junctions by comparing energy levels of josepshon energy to the normal charging energy. 
The josephson energy comes from kinetic energy of the tunneling electrons.

Martinis and Osborne state \cite[p.3]{martinis} that Josephson junction quantum computers are especially interesting because superconductors could provide long coherence times and because increasing the number of qubits should be straightforward.

@@

\begin{itemize}
    \item Often, as e.g. in the Josephson junction quantum computer, extremely low temperatures are needed. These have to be achieved at reasonable cost. Using e.g. laser cooling is a one approach in quantum computing. The concept of laser cooling was proposed by Steven Chu, Claude-Cohen-Tannoudji and William D. Phillips who got awarded the Nobel prize for their research in the develoment of methods to cool and trap atoms with laser light.
    \item Quantum algorithms have probabilistic characteritics. 
    This implies that in a single operation a quantum computer returns multiple solutions, each of those solutions with an assigned probability, where only one can be correct. 
    Figuring out the correct answer reduces the potential speed of quantum computers.
    \item Qubits are prone to errors earlier introduced as noise. 
    Noise can be caused e.g. by heat or noise in the environment. 
    As in classical computing, this noise can lead to bit-flips. There are approached in "quantum error correction" to deal with these errors. 
    One of those approaches is to use the "bit flip code" in which a total of 3 qubits are needed to result in 1 correct bit using quantum entanglement.  
    \item Increasing the number of qubits in a processor. The more qubits in a processor, the more logical qubits can be used. More qubits also lead to less errors since methods for error correction can be used more effectively.
    \item Decoherence leads to qubits retaining their quantum state only for a short period of time. 
    According to Mavroeidis \cite[p.3]{DBLP:journals/corr/abs-1804-00200} The longest time qubits remained in superposition so far was set by Australian researchers at the University of New South Wales. 
    Their qubits remained in superposition for a total of 35 seconds.
\end{itemize}

@@

\begin{subsection}{Shor's algorithm}
Shor's algorithm is a quantum computer algorithm and got developed by Peter Shor in 1994.
Essentially, it can find the prime factors of an integer in the complexity class BQP,
which is defined as the class of decision problems solvable by a quantum computer in polynomial time with an error probability of at most $\frac{1}{3}$ for all instances. 
Shor's algorithm is nearly exponentially faster than the general number field sieve, which is the most efficient known classical factoring algorithm.
The efficiency of the quantum Fourier transform which, as earlier discussed, can be caluclated using e.g. an ion trap quantum computer, is responsible for the efficiency of Shor's algorithm.
The algorithm is generally capable to break current public-key cryptography mechanisms as RSA or the Diffie-Hellman key exchange if the quantum computer could operate with little noise. 
That these algorithms could be vulnerable was already stated by Kirsch in 2015
\cite[p.6]{Kirsch2015QuantumCT}.

Bone and Castro \cite[p.6-9]{Bone} describe the workings of Shor's algorithm as follows. First, a memory register is placed into a superposition of all its possible states. Think of all possible permutations of $n$ bits existing in parallel.
A calculation performed with Shor's algorithm can be thought of as computations done in parallel for every of the permutations generated before. 
They then describe the mathematics performed on the registers: 
\begin{itemize} 
    \item N describes the integer to be factorized
    \item X is a random number in range $1 < X < N-1$
    \item X is raised to one of the permutations generated earlier.
    \item The remainder of this operation is placed in a second register. The first register contains the permutation.
\end{itemize}
After performing these operations on all permutations, it is noticable that the contents of the second register repeat e.g. for $N = 15$ the repeating sequence would be $1,2,4,8,1,2,4...$.
Now the frequency of repetition can be calculated by using a complex operation on the second register and the looking at the contents which causes the results from every permutation to interfere. A possible prime factor can then be calculated by using the frequency of repetition $f$:
\begin{equation}
Factor P = X^{\frac{f}{2}}-1
\end{equation}
The inteference that provides $f$ will lead to the correct answer with a high probability as incorrect answers cancel each other out when interfering. This cannot be guaranteed! Checking that the resulting number is correct can be achieved by performing a simple multiplication. Repeating the process for different random values X has then a high chance of revealing all prime factors.

@@

As Mavroeidis et al \cite[p.4]{DBLP:journals/corr/abs-1804-00200} state in their paper, Grover's algorithm can be utilized to find a collision in a hash function in $O(\sqrt{N})$ as searching for a collision is comparable to performing an unsorted search. 
Additionally, Grover's algorithm can be used to improve a lot of brute-force attacks targeting symmetric cryptography.
Brassard proved \cite{1998} that it is possible to combine Grover's algorithm with the birthday paradox, 
also known as a quantum birthday attack, which leads to finding collisions with a complexity of $O(N^{\frac{1}{3}})$.
As a result, many of current , rather weak, hashing alogithms are disqualified for use in the quantum era. 
However, as of 2021, both SHA-2 and SHA-3 with longer outputs remain quantum resistant as even Grover's algorithm does not make it feasible to to find a collision when the keys are too long.
\end{subsection}

@@

\begin{subsubsection}{Lattice-based Cryptography}
Lattice-based Cryptography is a form of public-key cryptography that avoids the weaknesses of RSA and related security mechanisms. 
Rather than multiplying primes, lattice-based encryption schemes involve multiplying matrices. 
As Micciancio and Regev mention in their paper \cite[p.2]{Micciancio2009}, 
lattice-based cryptographic mechanisms are based on the presumed hardness of lattice problems and it is belived that lattice-based cryptography cannot be cracked by a quantum computer since the frequency finding technique,
which is used in Shor's algorithm cannot be used in lattice-based problems. 
\end{subsubsection}
